Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 table_fpp.tex
FP table updates

\colhead{max($\delta_{\rm sec}$)} &
\colhead{AO?} &

@@

\colhead{$f_{p}$} &

@@

201555883.01 & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.6\times10^{-3}$ & $0.10$ & $3.6\times10^{-3}$ & Planet \\

@@

\enddata
\tablecomments{blurgh.}
\end{deluxetable*}

>>>>

\colhead{max($\delta_{\rm sec}$) [ppt]\tablenotemark{1}} &
\colhead{AO?\tablenotemark{2}} &

@@

\colhead{$f_{p}$\tablenotemark{3}} &

@@

 \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{a}\\

@@

\enddata
\tablecomments{blurgh.}
\tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
\tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
\tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
\tablenotetext{a}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
\end{deluxetable*}
